\documentclass[sans,letter]{moderncv}
\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\setlength{\hintscolumnwidth}{2.5cm}
\AtBeginDocument{\recomputelengths}


% personal data
\firstname{Thomas}
\familyname{Ernstorfer}
\address{355 Fulton St. Apt. \#102}{San Francisco, CA 94102}
\mobile{+1 (415)-463-9996}
\email{thomas@n0.cl}
%\extrainfo{Edad: 30 años\\Estado Civil: Soltero, sin hijos}
% optional, remove the line if not wanted
%\photo[64pt]{thomas.jpg}
%\quote{Fecha de nacimiento: 2 de Octubre de 1984}
%\nopagenumbers{} % uncomment to suppress automatic page numbering


% content
\begin{document}
\maketitle


\section{Education}

\cventry{2010}{BSc. Informatics (Ingeniería Civil en Informática)}
{Universidad Técnica Federico Santa María (UTFSM)}{Valparaíso, Chile}{
Thesis: \em ``Evaluating Eucalyptus As A Cloud Computing Platform.''
}{
Coursework: Programming Languages, Databases, Computer Networks, Computer Systems Architecture.
}


\section{Experience}

\cventry{Mar--May 2017}{Software Engineer}{Pivotus Ventures}
{Menlo Park, CA}{}
{\begin{itemize}
  \item Maintenance and enhancement of in-house Python to React Native transpiler.
  \item Technology used: Docker, MongoDB, Python, ReactJS.
\end{itemize}}

\cventry{Mar 2015\\--Feb 2017}{Senior Software Engineer}{AltX}
{San Francisco, CA}{}
{\begin{itemize}
  \item Application Team Lead, responsible for gathering requirements,
  architecture design, sprint planninig for new product features and
  technical debt reduction.
  \item Development of frontend and backend components for hedge fund
  screening, clustering, and fund performance analytics.
  \item Replace search system component in a monolitic backend with Elasticsearch.
  \item Technology used: AngularJS, Bootstrap, Docker, EhCache, Elasticsearch, Flask, MongoDB, Redis.
\end{itemize}}

\cventry{Feb 2013\\--Feb 2015}{Software Engineer}{SKOUT}
{Santiago, Chile and San Francisco, CA (since Oct. 2013)}{}
{\begin{itemize}
  \item Development of community management tools for internal use.
  Refactoring, performance analysis and update of existing community
  management platforms.
  \item Part of the team developing a new website frontend.
  \item Development of image cropping server.
  \item Technology used: AngularJS, AWS, Bootstrap, Django, MySQL, RabbitMQ, Redis.
\end{itemize}}

\cventry{Aug--Nov 2012}{Lead Developer}{Canubring.com}{Santiago, Chile}{}
{\begin{itemize}
  \item Design and development of a new version of the Canubring.com website.
  \item Handling of source code control and development guidelines.
  \item Managed external development for future iterations and
  applications.
  \item Technology used: Backbone.js, Bootstrap, Django, PostgreSQL, Python.
\end{itemize}}

\cventry{Apr--May 2012}{Consultant}{OctaneNation.com}{Santiago, Chile}{}
{\begin{itemize}
  \item Django development and templating of a new design for OctaneNation.com.
  \item Various bug fixes and system maintenance.
  \item Technology used: Bootstrap, Django, jQuery, MySQL, Python, Solr.
\end{itemize}}

\cventry{Jul 2011\\--Jan 2012}{Software Engineer}{Nimbic Chile}{Santiago, Chile}
{}{\begin{itemize}
  \item Design and development of the nCloud platform for EM circuit simulation
  over AWS clusters.
  \item Initial client-server design of Web EM CAD model viewer.
  \item Technology used: AWS, Boto, Bottle, ExtJS, jQuery, Python, MySQL.
\end{itemize}}

\cventry{Jan--May 2011}{Scalability Engineer}{SecondSense}
{Santiago, Chile}{}{\begin{itemize}
  \item AWS architecture design for a social audio streaming platform.
  \item Worked extensively on profiling and optimizing SecondSense's Mahout Slope One Recommender-based discovery service.
  \item Development of web frontend components.
  \item Technology used: Java, MySQL, PHP, Sprint, Solr, Tomcat, Zend.
\end{itemize}}

\cventry{2011--2013}{Part-time Teacher}
{Informatics Department, UTFSM}{Santiago, Chile}{}
{Introductory programming course for engineering students using the
python language.}

\section{Internships}

\cventry{Jan 2010\\Mar 2010}{Software Developer}{Intellicore}
{Viña del Mar, Chile}{}{\begin{itemize}
\item Developed the ``Travel Allowances'' web portal for Chile’s Ministry of Health in the Libertador General Bernardo O'Higgins Region.
\item Technologies used: Zend Framework, MySQL.
\end{itemize}}

\cventry{Dec 2006\\Jan 2007}{Software Developer}{BankBoston (now Itaú)}
{Santiago, Chile}{}{\begin{itemize}
  \item Made security and efficiency improvements to BankBoston's web access
  control application.
  \item Technologies used: Visual Basic 6, Microsoft SQL Server.
\end{itemize}}

\section{University}

\cventry{2008--2010}{Computer Systems Laboratory Assistant}
{Informatics Department, UTFSM}{Valparaíso, Chile}{}
{
\begin{itemize}
\item Applied networking experiences for students of the computer networks
course. Related system services administration and support.
\item Technologies used: Python, LDAP, Apache.
\end{itemize}
}

\cventry{2007--2010}{Teaching Assistant}
{Informatics Department, UTFSM}{Valparaíso, Chile}{}
{Teaching assistant for the programming course using the Pascal and Java programming
languages.}

\section{Technical Skills}
\cvcomputer{Languages}{Python, Javascript, Java}{Databases}{MySQL, PostgreSQL}
\cvcomputer{Web}{AngularJS, ReactJS}{Frameworks}{Django, Flask, Celery, Boto}
\cvcomputer{Cloud and Containers}{AWS, GCE, Docker}{Other Services}{Tomcat, RabbitMQ, Redis, Elasticsearch}
\cvcomputer{Source Control Management}{git, mercurial}{Operating Systems}{macOS, Debian and Redhat Linux distributions}

\end{document}
